\cvitem{Jan/2019-Present}{\textbf{Sr. Software Engineer}}
\cvitem{Company}{Hexaware Technologies}
\cvitem {Responsibilities}{As a Java Sr Full Stack Developer with Microservices, participated in the
analysis, design and development of different applications using Java and  REST W.S in the backend and React JS in the frontend,
also containerized  such applications using Docker and deploy them in Kubernetes.}
\cvitem {Highlights}{
\begin{description}
    \item[\ding{225}] {Design the architecture of a microservice  for authentication, such microservice was
        containerized in 3 Docker containers, one for the frontend, another for the backend and a 3rd
        one for the database.}
    \item[\ding{225}] {Principal developer of Authentication backend App, perform the analysis, design and development using
        Java 8, Spring MVC, Spring Data and Spring Security to generate the REST Services  used by the application.}
    \item[\ding{225}] {Principal developer of Authentication frontend App, perform the analysis, design and development using
        REACT JS, Redux and Axios to develop the view.}
    \item[\ding{225}] {Containerize backend, frontend and DB using Docker, create the Deployment and Services for the
        3 apps in order to deploy  and configure all 3 container in a Kubernetes Cluster and create a Jenkins pipeline to
        automatize the deployment process.}
    \item[\ding{225}]  Participate as a Sr Developer in Business Travel Assessment Application for Ernst and Young (EY),
        main activity was the creation of different endpoint for CRUD operations using  REST Web Services.
    % \item[\ding{225}] Ernst and young: DIFT  (Document Intelligence For Semi Structured documents )
    \item[\ding{225}] Analyze and configure the environment of Freddie Mac Selling System, analyze bugs
        and develop and deploy fixes using Java and Spring.
\end{description}
}


\cvitem{Aug/2014-Dec/2018}{\textbf{Technical Manager}}
\cvitem{Company}{HCL Technologies}
\cvitem {Responsibilities}{Manage a team 30+, delivering 40+ projects
  in over 4 years;
lead developer of 5+ Java Web applications.
Main achievements includes a ramp up from
three persons and one single project to over 30 persons working in 11 different projects
and successfully leading agile transformation.}

\cvitem {Highlights}{
\begin{description}
 \item[\ding{225}] Manage risks and opportunities, track and remove
   impediments and facilitate direct communication between developers and clients.
  \item[\ding{225}] Reduce dependency on onsite resources by
    decentralizing technical and domain knowledge from onsite resources and spreading it among nearshore and offshore team members.
  \item[\ding{225}] Substitute on-site management with nearshore
    management.
 \item[\ding{225}] Help employees to establish a career path and align it
   with Company objectives.
  \item[\ding{225}] Provide technical help to Developers, QA engineers
    and managers.
 \item[\ding{225}] Develop, Monitor and Implement training plan for new
   resources.
 \item[\ding{225}] Monitor software development life cycles, code quality and
   ensure high-quality project deliverables.
 \item[\ding{225}] Refactor USAA checking and saving web applications
 to fullfill EMV requirements.
 \item[\ding{225}] Develop application to automatize IRA  acquisition
 and withdraw process.
 \item[\ding{225}] Participate in the refactor all deposit (Checking, Saving, CD, and IRA)
 web applications for the pilot launch of the new rewards checking
 product - USAA Cashback Rewards Checking.
 \item[\ding{225}] Responsible for the development of Standalone Order Card Application.
\end{description}
}

\cvitem{Jul/2012-Jul/2014}{\textbf{Founder \& Principal Developer}}
\cvitem{Company}{Vulcano Software}

\cvitem {Responsibilities}{Legally constitute a corporation focused on
  providing custom software to SMEs. Manage all 
  phases of business and software development, including the creation of
  business strategy, financial planning, project management,  architectural design,
  requirement elicitation, analysis, coding, testing and delivery of
  the products.}

\cvitem {Activities}{
\begin{description}
 \item[\ding{225}] Estimate project cost and duration based on
   WBS, create and present cost proposals to clients and negotiate prices.
 \item[\ding{225}] Create software development and maintenance
   contracts.
 \item[\ding{225}] Architect and principal developer for all the
   applications of the company.
\end{description}}
\cvitem {Main Applications}{\begin{description}
 \item[\ding{225} Electronic Invoice System:] System used to manage
   bills, users, suppliers, and products;
 it generates and e-sign e-Invoices, in accordance with the requirements establish by
   Mexican Government.
 \item[\ding{225} Proprietary CMS for Web Pages:]
   Application that converts any static web page (based web standars) in dynamic page with a custom CMS, to generate
  the WYSIWYG CMS it is used the User UI as base and dynamically  add all the
   functionalities required to convert it to a WYSIWYG CMS.
\end{description}
}

%Create company from scratch
%Client management
%PRoduct planation
%Prodcut architecture 
%Analisys, design and development

%\vspace{3mm}

\cvitem{Jan/2012-Jun/2012}{\textbf{Sr. Developer}}
\cvitem{Company}{Enable}
\cvitem {Responsibilities}{Develop and maintained Vision Engager, a
  proprietary ERP based on Balance Score Card.}

\cvitem {Highlights}{
\begin{description}
 \item[\ding{225}] Responsible for the creation of one module used to
   show graphically the difference between real and projected objectives.
\item[\ding{225}] Main developer of a module  used in the the
  creation, management and display of Gantt diagrams.
\end{description}
}

%\vspace{3mm}

\cvitem{Nov/2009-Dec/2011}{\textbf{ Sr Developer.}}
\cvitem{Company}{KTC Agency}
\cvitem {Responsibilities}{Contribute to the development and testing
  of 10+ applications, main backend developer of  2 applications.}
\cvitem {Highlights}{
\begin{description}
 \item[\ding{225}] Lead back-end developer of "Coca Cola
   Happy Slider", an app used in
   "Coca Cola Choose Happiness" global marketing campaign.
    This application includes a analysis tool that helps to
   identify the correlation between customer moods and  international
   events. 
\item[\ding{225}] Responsible for the development of "Profuturo:
  Project your assets", a set of tools designed to automate the process of  trading and contracting retirement funds plans;
 it includes multiple
  simulators that let users take informed investment and
  saving decisions and a CMS for the "Project
  your assets" portal.
\end{description}
}
%\vspace{3mm}


\cvitem{Jul/2007-Oct/2009}{\textbf{ Jr Developer.}}
\cvitem{Company}{Cognosite S.C.}
\cvitem {Responsibilities}{Works as a Software Developer in Chrysler Mexico}
\cvitem {Highlights}{
\begin{description}
\item[\ding{225}] Design and development o a Kiosks management system
  for Chrysler plants in Mexico, this app allows Chrysler
  employees to look and print  personal and corporate documents, also
  allows managers to communicate advice and warnings to employees.
\end{description}
}
%\vspace{3mm}